--- 
title: "Statistical Programming Methods"
author: "James Balamuta"
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
site: bookdown::bookdown_site
description: ""
url: 'https\://coatless.github.io/statprogramming/'
github-repo: coatless/statprogramming
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
require(knitr)
read_chunk('r_book.R')
options(scipen = 8, width=65)
```

```{r load_packages, message=FALSE,echo=FALSE, warning=FALSE}
```

```{r misc_func, echo=FALSE}
```

# Preface
## A foreword

The book is a compilation of my *many* notes on programming. The material is not necessarily traditional as I have never really received **formal** computer science training. However, the hope is that it is at least helpful and/or provides an alternative explanation for the concepts under observation.

Any typos or other issues should be reported to [James Balamuta](mailto:balamut2@illinois.edu) forthwith.

##  Notation

## R Code

The code used throughout the book is R code. The R code should be able to used as-is. Alongside the PDF download of the book, you should find the R code used within each chapter. 
